---
title: "NHL API playground"
author: "Abishek Murali"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

"NHL and the NHL Shield are registered trademarks of the National Hockey League. NHL and NHL team marks are the property of the NHL and its teams. © NHL 2018. All Rights Reserved."


```{r}
library(httr)
library(jsonlite)
library(ggplot2)
library(tidyr)
library(dplyr)
library(purrr)
```

## Get data
```{r}
player_stats_NHL <- function(playerIDs){
  # This function accepts player IDs and output career stats
  # Args: playerIDs: Vector of Players IDS
  # output: Dataframe of player career stats
  
  #This defines URL for API
  base_url <- "https://statsapi.web.nhl.com/api/v1/people/"
  end_points <- "?expand=person.stats&stats=careerRegularSeason&expand=stats.team&site=en_nhl"
  
  #initialize empty dataframe for results
  ovr_stats <- data.frame()
  
  for(i in 1:length(playerIDs)){
    #Fetch data
    url_playa <- paste0(base_url,playerIDs[i],end_points)
    play_data <- GET(url_playa)
    play_df <- fromJSON(content(play_data,"text"))
    
    # Extract data from mind-numbingly nested dataframe. Check if the level of nestedness
    # can be found out programatically
    play_stats <- as.data.frame(play_df$people$stats)
    play_stats <- as.data.frame(play_stats$splits)$stat 
    play_stats <- cbind(Name = play_df$people$fullName,play_stats)
    
    if(i == 1){
      ovr_stats <- play_stats
    }else{
      ovr_stats <- rbind(ovr_stats,play_stats)
    }
    
  }
  return(ovr_stats)
}
```

## Using API

**To obtain player ID - Go to NHL.com and search for player name. In the URL the last 7 numbers indicate player ID. Copy that into the function argument.**

```{r}
player_op <- player_stats_NHL(c(8478402,8471675,8471214,8476453,8477492,8471685))
```

## Comparing goals and assists per game

```{r}
ggplot(player_op) +
  geom_col(aes(x = Name,y = points/games),width = 0.3) +
  geom_text(aes(x = Name,y = points/games + 0.04 ,label = round(points/games,2))) +
  coord_flip() +
  labs(title = "Points per games")
```


```{r}
ggplot(player_op) +
  geom_col(aes(x = Name,y = goals/games),width = 0.3) +
  geom_text(aes(x = Name,y = goals/games + 0.04 ,label = round(goals/games,2))) +
  coord_flip() +
  labs(title = "Goals per games")
```
```{r}
ggplot(player_op) +
  geom_col(aes(x = Name,y = assists/games),width = 0.3) +
  geom_text(aes(x = Name,y = assists/games + 0.04 ,label = round(assists/games,2))) +
  coord_flip()+
  labs(title = "Assists per games")
```

